Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-18 article.tex
added definitions table

Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}. Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}. The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}. Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
\subsection{Literature Review}
#TODO:
\subsection{Bayesian Networks}

@@

\subsection{CPT Interpolating}

@@

@@

\subsection{The problem}
\subsubsection{Not understanding the problem context, complexity without value.}
It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
\begin{enumerate}
        \item what do you want to reason about?
        \item What dont you know?
        \item What information do you have?
        \item What do you know?
These questions are well addressed in prior research. The creation of baseline models showed strong linear relationships between many variables. The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability. here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
\subsubsection{Complexity without value}
A very common impulse, when something is known about the problem, is to want to put it in the model. But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value). Instead, the knowledge engineer must focus on the problem:
"Which of the known variables are most relevant to the problem?"
- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
\end{enumerate}
\subsection{Structure - Nodes}
The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
\begin{enumerate}
        \item Getting the node values wrong
        \item Node values aren't exhaustive
        \item Node values aren't mutually exclusive
        \item Incorrect modelling of mutually exclusive outcomes
        \item Trying to model fuzzy categories
        \item Confusing state and Probability
        \item Confusion about what the node represents
\end{enumerate}
Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
\subsection{Structure Arcs}
\subsubsection{Getting the arc directions wrong}
Arc directions are commonly wrong for the following reasons:
\begin{enumerate}
        \item Modelling reasoning rather than causation
        \item Inverting cause and effect
        \item Missing variables
\end{enumerate}
To note: Korb and Nicholson do not actually suggest a method for overcoming these problems. There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation. It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
\subsubsection{Too many parents}
Sometimes it is unavoidable that a node is affected by many factors, or other nodes. There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child. This technique was employed in the creation of the structure of the BN with the expert panel.
\subsection{Parameters}
\subsubsection{Experts estimates of probabilities are biased}
\begin{enumerate}
        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison. "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.

@@

\subsection{Industry definitions}
How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
Results: Use the agreed upon definitions to fully realise factors and their impact.

\ref{table:definitions}

>>>>

Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}. Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}. The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}. Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.

\subsection{Literature Review}
#TODO:

\subsection{Bayesian Networks}

@@

\subsection{CPT interpolating}

@@

% FIXME: should I extrapolate on this method?

@@

\subsection{The problem}
\subsubsection{Not understanding the problem context, complexity without value.}
It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
\begin{enumerate}
        \item what do you want to reason about?
        \item What dont you know?
        \item What information do you have?
        \item What do you know?
These questions are well addressed in prior research. The creation of baseline models showed strong linear relationships between many variables. The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability. here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
\subsubsection{Complexity without value}
A very common impulse, when something is known about the problem, is to want to put it in the model. But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value). Instead, the knowledge engineer must focus on the problem:
"Which of the known variables are most relevant to the problem?"
- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
\end{enumerate}

\subsection{Structure - Nodes}
The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
\begin{enumerate}
        \item Getting the node values wrong
        \item Node values aren't exhaustive
        \item Node values aren't mutually exclusive
        \item Incorrect modelling of mutually exclusive outcomes
        \item Trying to model fuzzy categories
        \item Confusing state and Probability
        \item Confusion about what the node represents
\end{enumerate}
Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.

\subsection{Structure Arcs}
\subsubsection{Getting the arc directions wrong}
Arc directions are commonly wrong for the following reasons:
\begin{enumerate}
        \item Modelling reasoning rather than causation
        \item Inverting cause and effect
        \item Missing variables
\end{enumerate}
To note: Korb and Nicholson do not actually suggest a method for overcoming these problems. There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation. It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
\subsubsection{Too many parents}
Sometimes it is unavoidable that a node is affected by many factors, or other nodes. There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child. This technique was employed in the creation of the structure of the BN with the expert panel.

\subsection{Parameters}
\subsubsection{Experts estimates of probabilities are biased}
\begin{enumerate}
        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison. "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.

@@

\subsection{Industry definitions}

How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
Results: Use the agreed upon definitions to fully realise factors and their impact.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\ref{table:definitions}
    \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Variable name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule
    \textbf{Water use} & Total amount of water used by a vineyard in a financial year (ML/Ha) & \textbf{Low} & High \\
    \textbf{Agrochemical type} & When selecting agrochemicals, those which are less hazardous to beneficial organisms and/or have a lower environmental impact are considered & \textbf{Yes} & No \\
    \textbf{Spray application number} & Number of foliar spray applications used to control pests and diseases (spray applications/Ha/FY) & \textbf{Low} & High \\
    \textbf{Agrochemical legislation} & The legislated regulations regarding agrochemical use as specified by the APVMA. Dog book recommendations are further restrictions for export wine production and to protect the reputation of Australian wine. & \textbf{Yes} & No \\
    \textbf{Vineyard floor management} & Proportion of vineyard floor covered with a cover crop. & High & \textbf{Low} \\
    \textbf{Pest and disease management methods} & All available methods of management are considered before a management program is chosen (i.e. biological, chemical, cultural, mechanical, and technological) & \textbf{Yes} & No \\
    \textbf{Electricity use} & Total amount of electricity used by a vineyard in a financial year (kWh/Ha) & \textbf{Low} & High \\
    \textbf{Electricity Price} & The unit cost of electricity purchased by a vineyard & \textbf{Low} & High \\
    \textbf{Renewable energy} & Percentage of energy that is renewable & High & \textbf{Low} \\
    \textbf{GHG emissions} & Total amount of GHG emission produced by a vineyard in a financial year (Kg CO2e/Ha) as calculated  by NGA legislation & \textbf{Low} & High \\
    \textbf{Environmental Impact} & The positive/negative impact a vineyard has on its immediate environment (to gate). & \textbf{Ideal} & Not Ideal \\
    \textbf{Fertiliser use} & Total amount of nitrogen (synthetic and organic) used by a vineyard in a financial year (Kg/Ha) & \textbf{Low} & High \\
    \textbf{Fuel use} & Total amount of fuel (diesel, petrol, lpg and biodiesel) used by a vineyard in a financial year (L/Ha) & \textbf{Low} & High \\
    \textbf{Renewable Fuel} & Percentage of fuel used that is renewable. & High & \textbf{Low} \\
    \textbf{Grape Price} & Grape price per tonne & High & \textbf{Low} \\
    \textbf{Nutrient leaching management} & The depletion of nutrients in the grapevine root zone is minimised through best practice irrigation scheduling and soil moisture monitoring. & \textbf{Yes} & No \\
    \textbf{Market supply and demand} & The relationship between the quantity of winegrapes produced and the quantity that consumers wish to buy & High & \textbf{Low} \\
    \textbf{Pest and Disease Management} & The management of pests and diseases such as through the employ of fungicide and pesticides & \textbf{Yes} & No \\
    \textbf{Soil degradation management} & Areas at risk of degradation via compaction or erosion are identified and actions to remediate and minimise degradation are taken (i.e. don’t traffic waterlogged soils, minimise cultivation, maintain vineyard floor cover with cover crops, etc.) & No & \textbf{Yes} \\
    \textbf{Soil organic carbon management} & Areas with low or declining soil organic carbon levels are identified and actions to improve soil carbon levels are taken (i.e. minimise cultivation, maintain vineyard floor cover with cover crops, apply mulch or compost, etc.) & \textbf{Yes} & No \\
    \textbf{Tractor passes} & The number of times a tractor passes over the whole vine row area & \textbf{Low} & High \\
    \textbf{Water use efficiency} & The amount of water used per tonne of grapes produced & High & \textbf{Low} \\
    \textbf{Water licences} & Current water licences and permits are adhered to & \textbf{Yes} & No \\
    \textbf{Water Price} & The cost per unit of water paid for by a vineyard & \textbf{Low} & High \\
    \textbf{Water quality} & Water used for irrigation is assessed annually for quality (pH, chloride, sodium absorption ratio, electrical conductivity, soluble solids, hardness, microbial contamination). Water that may case soil degradation or irrigation inefficiency is treated before use. & \textbf{Yes} & No \\
    \textbf{Water Scarcity} & Whether the country is suffering drought or not (s defined by BOM) & No & \textbf{Yes} \\
    \textbf{Weather Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
    \textbf{Grape quality and yield targets} & The yield and quality targets of a vineyard block as outlines in the grape supply contract. & \textbf{Ideal} & Not Ideal \\
    \textbf{Agrochemical score} & Agrochemicals with high human and environmental hazard scores are avoided. & \textbf{Yes} & No \\ \bottomrule
    \end{tabular}
\end{table}
